Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-04-20 paper/current/main.tex
updating SI text section numbers
other minor changes

When scientists move, they bring their knowledge with them, and so understanding the flows of scientists allows us to understand the flow of knowledge around the world. 
However, given its complexity~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, new approaches are needed to make sense of landscape of global scientific mobility. 
A basic component of mobility is distance--people are more likely to move nearby than to cross continents.
Although many alternative ways to quantify the distance exist~\autocite{boschma2005proximity}, geographic distance remains the unambiguous and foundational quantity.
In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance.
However, distance is not always so straightforward as simple geography. 
Geographic distance alone fails to capture the host of historical, linguistic, cultural, and cognitive distances that also drive mobility. 
For instance, Australia may be physically close to Indonesia, but in terms of language, history, and shared culture, they are essentially neighbors to the United Kingdom.
Then, how can we quantify meaningful, useful distance between institutions, cities, and countries?

@@

%
% Figure - Example of mobility sentences
%
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\textwidth]{\figdir/mobility_example_combined.pdf}
    \caption{
        \textbf{Co-affiliation trajectories represented as sentences}
        \textbf{a.}
        An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
        To each organization, a unique identifier is assigned, and they are assembled into a mobility sentence ordered by year of publication.
        \textbf{b.}
        In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$. 
        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or "epoch" of the \textit{word2vec} model. 
    }
    \label{fig:methods:mobility_sentence}
\end{figure}

@@

%
%
\paragraph*{S1 Text}
\label{si:text:mobility_models}
{\bf Modeling scientific mobility.}
There are many ways of modeling scientific mobility from bibliographic data, the first consideration being the unit of analysis. 
Most studies of mobility have focused on \textit{country-level} mobility--the flows of researchers across nations~\autocite{sugimoto2017mostimpact, scellato2015migrant, robinson-garcia2018indicators, franzoni2012foreign-born}.
Practically, country-level analyses benefit from higher reliability, such that such that idiosyncrasies and errors inherent to bibliographic databases are mitigated by this higher level of aggregation.
Epistemically, country-level analysis is useful for national science governance who aim to understand the status of their country in the global landscape and make informed policy decisions. 
Analyses at lower levels of analysis are far less common. 
\textit{Regional}-level scientific mobility--the flow of researchers between regions or cities within or across countries, has been only minimally studied~\autocite{vaccario2019mobility}, possibly due to lack of reliable long-term data and lack of policy relevance to national-level lawmakers. 
\textit{Organization}-level mobility has potential to inform institutional policy and for understand the composition of mobility within a single country or region, especially as it relates to organization performance, prestige, and inequality~\autocite{albarran2017topeconomic, deville2014career, morgan2018prestige, clauset2015hierarchy}.
However, affiliation disambiguation and noise in bibliometric data has makes large-scale organization-level analysis challenging.
Here, we learn neural-network embeddings of scientific mobility at the level of organizations using a curated bibliographic database.
These embeddings are robust to noise, and so are capable of representing clear structure even amid issues with organizational disambiguation. 
In doing so, embeddings also capture a more detailed understanding of mobility than has been previously studied.

@@

%
% S1 TEXT
\paragraph*{S1 Text}
\label{si:text:mobility_traj}
{\bf Building mobility trajectories.}

@@

%
% S1 TEXT
\paragraph*{S1 Text}
\label{si:text:ppr_dist}
{\bf Network-based personalized page rank distances.}

@@

%
% S2 TEXT
\paragraph*{S2 Text}
\label{si:text:organizations}
{\bf Organization disambiguation and metadata.}

@@

%
% S3 TEXT
\paragraph*{S3 Text}
\label{si:text:disambiguation}
{\bf Author name dismabiguation.}

>>>>

When scientists move, they bring their knowledge with them, and so understanding the flows of scientists allows us to understand the flow of knowledge around the world. 
However, given its complexity~\autocite{robinson2019mobility, vannoorden2012mobility, deville2014career, ackers2008mobility, scott2015dynamics}, new approaches are needed to make sense of landscape of global scientific mobility. 
A basic component of mobility is distance--people are more likely to move nearby than to cross continents.
Although many alternative ways to quantify the distance exist~\autocite{boschma2005proximity}, geographic distance remains the unambiguous and foundational quantity.
In turn, models of human mobility, such as the Gravity~\autocite{zipf1946gravity} and Radiation models ~\autocite{simini2012universal}, rely almost exclusively on geographic distance.
However, distance is not always so straightforward as simple geography. 
Geographic distance alone fails to capture the host of historical, linguistic, cultural, and cognitive distances that also drive mobility. 
For instance, Australia may be physically close to Indonesia, but in terms of shared language, history, and culture, they are essentially neighbors to the United Kingdom.
Then, how can we quantify meaningful, useful distance between institutions, cities, and countries?

@@

%
% Figure - Example of mobility sentences
%
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\textwidth]{\figdir/mobility_example_combined.pdf}
    \caption{
        \textbf{Co-affiliation trajectories represented as sentences}
        \textbf{a.}
        An author published five papers across five time periods, with only one affiliation listed in the byline of each paper.
        To each organization, a unique identifier is assigned, and they are assembled into a mobility sentence ordered by year of publication.
        \textbf{b.}
        In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$. 
        In the case where multiple organizations are listed within the same year, then organization IDs within a single year are randomized across each training iteration or "epoch" of the \textit{word2vec} model (for more detail, see Supporting Materials). 
    }
    \label{fig:methods:mobility_sentence}
\end{figure}

@@

%
% S2 Text
\paragraph*{S2Text}
\label{si:text:mobility_models}
{\bf Modeling scientific mobility.}

There are many ways of modeling scientific mobility from bibliographic data, the first consideration being the unit of analysis. 
Most studies of mobility have focused on \textit{country-level} mobility--the flows of researchers across nations~\autocite{sugimoto2017mostimpact, scellato2015migrant, robinson-garcia2018indicators, franzoni2012foreign-born}.
Practically, country-level analyses benefit from higher reliability, such that such that idiosyncrasies and errors inherent to bibliographic databases are mitigated by this higher level of aggregation.
Epistemically, country-level analysis is useful for national science governance who aim to understand the status of their country in the global landscape and make informed policy decisions. 
Analyses at lower levels of analysis are far less common. 
\textit{Regional}-level scientific mobility--the flow of researchers between regions or cities within or across countries, has been only minimally studied~\autocite{vaccario2019mobility}, possibly due to lack of reliable long-term data and lack of policy relevance to national-level lawmakers. 
\textit{Organization}-level mobility has potential to inform institutional policy and for understand the composition of mobility within a single country or region, especially as it relates to organization performance, prestige, and inequality~\autocite{albarran2017topeconomic, deville2014career, morgan2018prestige, clauset2015hierarchy}.
However, affiliation disambiguation and noise in bibliometric data has makes large-scale organization-level analysis challenging.
Here, we learn neural-network embeddings of scientific mobility at the level of organizations using a curated bibliographic database.
These embeddings are robust to noise, and so are capable of representing clear structure even amid issues with organizational disambiguation. 
In doing so, embeddings also capture a more detailed understanding of mobility than has been previously studied.

@@

%
% S3 TEXT
\paragraph*{S3 Text}
\label{si:text:mobility_traj}
{\bf Building mobility trajectories.}

@@

%
% S4 TEXT
\paragraph*{S4 Text}
\label{si:text:ppr_dist}
{\bf Network-based personalized page rank distances.}

@@

%
% S5 TEXT
\paragraph*{S5 Text}
\label{si:text:organizations}
{\bf Organization disambiguation and metadata.}

@@

%
% S6 TEXT
\paragraph*{S6 Text}
\label{si:text:disambiguation}
{\bf Author name dismabiguation.}
